Visualizing probability distributions across bivariate cyclic temporal granularities

### 2021-04-14 reviews/response.Rmd

---
title: Response to reviewers
author: "JCGS-20-344"
output:
  MonashEBSTemplates::memo:
    includes:
fontfamily: mathpazo
---

@@

Q4. $w$ in $T_w$ is not well defined for circular granularities in Section 3.2 & 3.5. The definition of $T_w$ uses $T_w$  itself in the formula making it hard to understand. Relevantly, what is the interpretation of $k$ where w = 0; 1; :::; k-1? In my opinion, the number of cycles
should be defined for cyclic granularities, for example, $w_{B,G}(z) = \lfloor z/P(B;G) \rfloor$, which
represent the cycle that the granule is in.

A4.

## Places that need clarification

Q1. Page 7, Definition 6. Is "the number of granules of H" finite or infinite? If each granule $G(i)$ has the index $i \in Z_{>=0}$, then the phrase is similar as "the number of non-negative integers."

A1. Number of granules of $H$ should be finite. Question

Q2. Page 7, Lines 19-20. It is claimed that quasi-periodic relationship has a finite number of periods where granularities behave in an anomalous way. What does the finite number of periods mean and why is it finite? Does it mean a finite number of granularity groupings? Does it mean a finite number of irregular cycles? By Definition 4 of Bettini & De Sibi (2000), $E_1, . . . , E_z$ are the granularity exceptions, but the number of granularity exceptions does not have to be finite.

A2. "Number of periods" rephrased as "spans of time". Bettini & De Sibi (2000) states in P57 L17 while introducing quasi-periodic relationships that " except for a finite number of spans of time where they behave in an anomalous way."

Q3. Page 8, Definition 8, what is the "period" P(B,G)? Is it same as P in Definition 6? Is it a mapping or function?

It is the same but stressed to make it clear that the period will be a "function" of two granularities $B$ and $G$.

Q4. Page 10, Line 14, Q4 week-of-month is probably not a good example for quasi-circular granularities. By Definition 4, week cannot be grouped into month, because there could exist $week(i) \subset month(j)$ when the $i^{th}$ week crosses two months. Similarly, week is not finer than month by Definition 5. Since periodicity is defined on top of grouping, and circular is defined on top of periodicity, the scenario of Q4 cannot be defined. On the other hand, the period length for week-of-month is not an integer, but it is an integer for Q1 - Q3.

A4. That's right. Alternatively, if we define the linear granularity week such that a week ends when a month ends, then week groups into months in a quasi-periodic way where the period length of week-of-month would be either 4 or 5, since any month could only be composed of either 4 or 5 weeks. week-of-month is a cyclic granularity that could be important for certain contexts and hence it makes sense
to define weeks like that. The first, second, third week-of-month corresponds to first, second, third quarter of the month and so on.

Q5.  Page 10, Definition 9, is R' similar as the period P of the grouping (B,G')? Is R' a constant or variable with irregular mapping?

A5. R' is the number of granules of G' in the period P. For example, the grouping (day, month) has period 365 (ignoring leap years), then R = 12, since there are 12 months in 365 days. Given a period, R' is constant.

Q6.  Page 11, Definition 10, what is the interpretation of n where i = 1, ..., n?

n is the number of Aperiodic linear granularities.

Q7. Page 14, Lines 26-27. Is z the original index for the bottom granularity? If yes, why $C_{katun, baktun}(z) = \lfloor 18 × 20 × z/20 \rfloor mod 20$? Shouldn't it be $z mod 20$? If not, then what is $z$? By Definition 8, $z \in Z$ is the original time index based on the bottom granularity, but here $z$ seems to be defined as the time index based on granularity katun.

A7. $z$ is the original index for the bottom granularity $kin$. So, $C_{kin, uinal}(z) = z mod 20$. For $C_{katun,baktun}(z)$, we first need to have katun in terms of kin through the operation $18*20*z/20$

Q8.  Page 11, lines 22-33. The explanation of Figure 3 is confusing. If the week-of-the- semester week type is a quasi-circular granularity, then the day-of-the-semester week type can be also quasi-circular granularity, as all days are nested in weeks. Actually the notation should not be "week-of-the-semester week type", but "semester week-of-the- semester week type". The relationship between G and H should be clarified. It will be clearer if the authors can make a granularity "semester day" (U) from B. Therefore we have the following granularities.
*$Q_{H,M}$ : quasi-circular granularity, 
semester week -of-the-semester week type
*$Q_{U,M}$ : quasi-circular granularity, semester day-of-the-semester week type.

Page 20, Line 47, "for weekdays the interquartile range of consumption reduces over the year, whereas this pattern is not true for weekends" is hard to be justified. By Figure the IQR is given by the height of blue (LV=F) boxes. They are the largest in Quarter 2 and smallest in Quarter 4 for both weekdays and weekends.

rephrased.

### 2021-04-14 reviews/response.Rmd

Q3. What is the definition of aperiodic linear granularities? On Page 11, Definition 10, $M_i$ are aperiodic linear granularities. If $M_i$ are aperiodic, then is $M$ also an aperiodic linear granularity? What is the relationship between aperiodic linear granularity and aperiodic
cyclic granularity?

A3. Aperiodic linear granularities are those that can not be defined by Definition 6. If $M_i$ is periodic, then $M = \bigcup M_i$ is periodic, but if each $M_i$'s are aperiodic, then $M$ could be periodic or aperiodic. In Definition 10, we want $M$ to be aperiodic. Definition 10 and introduction of Section 3.3 briefly rephrased to improve clarity.

Q4. $w$ in $T_w$ is not well defined for circular granularities in Section 3.2 & 3.5. The definition of $T_w$ uses $T_w$  itself in the formula making it hard to understand. Relevantly, what is the interpretation of $k$ where w = 0; 1; :::; k-1? In my opinion, the number of cycles
should be defined for cyclic granularities, for example, $w_{B,G}(z) = \lfloor z/P(B;G) \rfloor$, which
represent the cycle that the granule is in.

A4. R' is the number of granules of $G'$ in each cycle.
If $z$ belongs to $k^{th}$ granule of $G'$, then $z \in T_k$. Here $w \mod R'$ represents the index that must be shifted to obtain $G'(w)$. The idea here is if we know the composition of each of the granules of $G'$ in terms of granules of $B$ for one cycle, we can find the composition of any granule of $G'$ beyond a cycle since the "pattern" repeats itself along the time domain due to the periodic property. The periodic property also ensures that $\vert T_w \vert = \vert T_{w\mod R'} \vert$ since every $w^{\text{th}}$ and $(w+R')^{\text{th}}$ granule of $G'$ will have the same number of granules of $B$. The term $\sum_{w=0}^{k-1}\vert T_{w}\vert$ denotes the number of granules of $B$ till the $(k-1)^{\text{th}}$ granule of $G'$. Since $\vert T_w \vert = \vert T_{w\mod R'} \vert$, the number of granules of $B$ till the $(k-1)^{\text{th}}$ granule of $G'$ becomes $\sum_{w=0}^{k-1}\vert T_{w \mod R'}\vert$ in Definition 9.

### 2021-04-20 main.Rmd
definition 6 - added finite granularity and Z_>=0

\begin{definition}\label{def:periodical}
A granularity $G$ is \textbf{periodical} with respect to a granularity $H$ if:
(1) $G \trianglelefteq H$; and
(2) there exist $R$, $P \in \mathbb{Z}_+$, where $R$ is less than the number of granules of $H$, such that for all $i \in \mathbb{Z}$, if $H(i) = \bigcup_{j \in S}G(j)$ and $H (i + R) \neq \phi$ then $H (i + R) = \bigcup_{j \in S} G(j + P)$.
\end{definition}

>>>>

\begin{definition}\label{def:periodical}
A granularity $G$ is \textbf{periodical} with respect to a finite granularity $H$ if:
(1) $G \trianglelefteq H$; and
(2) there exist $R$, $P \in \mathbb{Z}_+$, where $R$ is less than the number of granules of $H$, such that for all $i \in \mathbb{Z_\geq 0}$, if $H(i) = \bigcup_{j \in S}G(j)$ and $H (i + R) \neq \phi$ then $H (i + R) = \bigcup_{j \in S} G(j + P)$.
\end{definition}
